Mallows, Black-box combinatorial optimization, limited budget, ???

### 2020-09-10 paper/main.tex
a bit of intro

In many practical optimization problems, the objective function contexts
% minimize the uncertainty in the final solutions or

>>>>

In many practical optimization problems, the objective function is not
explicitly available and solutions are evaluated by means of expensive
prediction models, simulations or physical experiments. When decision variables
are continuous, the use of Bayesian surrogate-models, e.g., Gaussian processes,
in optimization has become widespread~\citep{JonSchWel98go,ForKea2009surrogate}. Motivated by this success, there have been attempts at adapting such surrogate models to the combinatorial case~\citep{ZaeStoBar2014:ppsn,ZaeStoFriFisNauBar2014},

% minimize the uncertainty in the final solutions or
